---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# swfcalib

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/slurmworkflow)](https://CRAN.R-project.org/package=slurmworkflow)
[![R-CMD-check](https://github.com/EpiModel/swfcalib/workflows/R-CMD-check/badge.svg)](https://github.com/EpiModel/swfcalib/actions)
[![codecov](https://codecov.io/gh/EpiModel/swfcalib/branch/main/graph/badge.svg?token=eo2r0HeP8Z)](https://codecov.io/gh/EpiModel/swfcalib)
<!-- badges: end -->

`swfcalib` gives a scaffold to make an automated calibration system on a
[Slurm](https://slurm.schedmd.com/) equipped HPC.

`swfcalib` does not use a long running job to orchestrate the calibration but
relies on [`slurmworkflow`](https://github.com/EpiModel/slurmworkflow) and a
stored calibration object to chose which step of the calibration to run. This
allows very long calibrations to take place without flooding the `slurm` queue.

## Installation

You can install the development version of **swfcalib** like so:

``` r
remotes::install_github("EpiModel/swfcalib")
```

## Example

```{r example, eval = FALSE}
library(swfcalib)
```

## Design

The calibration process follows a typical proposal, validation loop. Where
the model is run with a set of parameters and a new proposal is made according
to the results. This goes on until the model is fully calibrated.

The specificity lies in the ability to try many proposal at once on an HPC, and
to set up this proposal validation loop without a long running orchestrating
job.

The calibration can be splited into *waves*. Each wave can contains multiple
*jobs*, each focusing on a set of parameters. This permits the parallel
calibration of multiple independent parameters. At each *iteration*, the model
is ran only once per proposal, and each job gather the outcomes it needs to
make its next proposal. Once all *jobs* in a *wave* are done, i.e. the
parameters the govern are calibrated, the system moves to the next *wave*. This
allows the sequential calibration of parameters when strong assumption about
their independence can be made.

This design was crafted for the very noisy models where many replications are
needed and where most parameters are independent or conditionally independents.

## Terminology

- the *model*: a function taking a *proposal* as argument and returning
  formatted *results*. It is what we are calibrating.
- a *proposal*: a one row `data.frame` with each column being a parameter for
  the *model*
- *results*: the output of a *model* run for a given *proposal*.
- *sideload*: data saved by a job to be reused at the next or in a later part
  of the current iteration
- *job*: a set of parameters to be calibrated at once. I.e. using the same
  proposal function and the same checker function
- *wave*: a set of independent *jobs* that can be calibrated using the same run
  of the model.
